Robust DPG stability II

### 2012-04-02 docs/NewBCRobustness_paper/paper.tex
began restructuring of paper, added to bibliography
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@415 36274a68-8941-4c93-80ef-affaed5139da

\textcolor{red}{add bit about residual-based stabilization terms and test functions}

@@

The DPG (discontinuous Petrov-Galerkin) method is the combination of the concept of computable optimal test functions with the so-called ``ultra-weak formulation", where the regularity requirement on each solution variable is relaxed through integration by parts.  Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.  The result is a hybridized DG method with locally supported optimal test functions.  For a given operator equation $Au = f$, the ultra-weak formulation is 
\[
b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, v \rangle - (u,A^*v) - (f,v)
\]
where $A^*$ is the formal adjoint resulting from integration by parts.

@@

Under the assumption of injectivity of the adjoint of our variational operator $B$, we can define the \textit{optimal test norm} 
\[
\|v\|_{\rm opt} = \sup_{u\in U}\frac{b(u,v)}{\|u\|_U}
\]
If the solution is in $U$, then choosing $\|v\|=\|v\|_{\rm opt}$ implies $\|u\|_E = \|u\|_U$. The proof is simple; we have by definition that $b(u,v) \leq \|u\|_U\|v\|_V$. The reverse $b(u,v) \leq \|u\|_U\|v\|_V$ is proved by
\[
\inf_{u\in U} \frac{\|u\|_E}{\|u\|_U} = \inf_{u\in U} \sup_{v\in V}\frac{b(u,v)}{\|v\|_V\|u\|_U} = \inf_{v\in V} \sup_{u\in U}\frac{b(u,v)}{\|v\|_V\|u\|_U} = \inf_{v\in V} \frac{\|v\|_V}{\|v\|_V} = 1
\]
where we're able to switch the order of $\inf$ and $\sup$ due to the injectivity of $B$ (see  \cite{BabuskaEquivBrezzi}). This is the ideal test norm; given any particular norm $\|u\|_U$, DPG under the optimal test norm will return the best finite element approximation in that norm.

The norm $\|v\|_{\rm opt}$ is non-localizable, however - the inversion of the inner product corresponding to this norm is global, and solving for optimal test functions under this optimal norm will result in global problems as well, due to the coupling given by the boundary terms in our bilinear form.  In practice, an approximation is made by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables, producing so-called \textit{quasi-optimal} test norms.  The DPG method is currently being analyzed for both acoustic and elastic waves in context of the Helmholtz equation and equations of linear elasticity.  Numerically, DPG appears to provide a ``pollution-free" method without phase error for these problems under the ``quasi-optimal" test norm with a specific scaling of the regularizing $L^2$ terms \cite{DPG4}. Similar results have also been obtained with the quasi-optimal test norm in the context of the elasticity \cite{DPGElas} and linearized Stokes equations \cite{Camellia}.

@@

We consider the model convection-diffusion problem on domain $\Omega$ with boundary $\Gamma$
\begin{align}
\div (\beta u) - \epsilon\Delta v &= f  \label{primal}
\end{align}
in first order form
\begin{align*}
\div (\beta u - \sigma) &= f  \\
\frac{1}{\epsilon}\sigma - \grad u &= 0
\end{align*}
with the corresponding variational form 
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle 
\end{align*}
where $\left[ \tau_n \right]$ and $\left[ v\right]$ denote the jumps in $\tau_n$ and $v$, defined as
\begin{align*}
\left[ \tau_n \right] &= \tau^+ \cdot n^+ + \tau^-\cdot n^-\\
\left[ v\right] &= v^+{\rm sgn}(n^+) + v^-{\rm sgn}(n^-)
\end{align*}
Additionally, the inner products are taken element-wise over the finite element mesh $\Omega_h$, and the duality pairings are taken on $\Gamma_h$, the mesh ``skeleton", or union of edges of elements $K$ in $\Omega_h$.  The divergence and gradient operators are likewise understood to act element-wise.

@@

Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we can now also define the trace norms as (canonical) minimum energy extension norms 
\begin{align*}
\|\widehat{u}\| &= \inf_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gamma_h\setminus \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}\\
\|\widehat{f}_n\| &= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}= 0, \left. q\cdot n \right |_{\Gamma_h} = \widehat{f}_n} \|q\|_{H({\rm div},\Omega)}
\end{align*}
Additionally, throughout the rest of this work, we denote norms on $u$ and $\sigma$ as
\begin{align*}
\|u\| &= \|u\|_{L^2} \\
\|\sigma\| &= \|\sigma\|_{L^2}
\end{align*}
We will construct norms on $U$ as combinations of norms on each variable
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
\]
\subsection{Norms on $V$}

%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega_h$. 
As $\tau \in H({\rm div},\Omega_h)$ and $v \in H^1(\Omega_h)$, we will construct norms on $v$ and $\tau$ using some combination of terms which are equivalent to the canonical broken $H^1(\Omega_h) \times H({\rm div},\Omega_h)$ norm 
\[
\|\left(\tau,v\right)\|_{H^1(\Omega_h) \times H({\rm div},\Omega_h)} = \|v\|_{L^2(\Omega_h)}^2 + \|\grad v\|_{L^2(\Omega_h)}^2  + \|\tau\|_{L^2(\Omega_h)}^2 + \|\div \tau\|_{L^2(\Omega_h)}^2
\]
The exact norms that we will place on $V$ will be determined later.

The boundary norms on $\Gamma_h$ for $v$ and $\tau$ are defined by duality from the bilinear form
\begin{align*}
\|[\tau\cdot n]\| &= \|[\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
\|[v]\|&=\|[v]\|_{\Gamma_h^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div};\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
\end{align*}

@@

For convection-diffusion, the quasi-optimal norm is 
\[
\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v \|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 + C_1\|v\|_{L^2} + C_2\|\tau\|_{L^2}
\]
for some choice of constants $C_1$ and $C_2$.  We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.  However, use of this norm for the convection-diffusion problem is difficult - the variational problem for optimal test functions using the quasi-optimal test norm is equivalent to a reaction-diffusion system \cite{DBLP:journals/procedia/NiemiCC11}.  Transforming the problem to the reference element reveals that will induce strong boundary layers of width $\epsilon/h^2$ (in comparison, in Helmholtz and wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in smooth optimal test functions that are much easier to approximate over the reference element).  As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on partially under-resolved meshes is unavoidable.

Resolving such boundary layers for an underresolved mesh has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.  However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is difficult and far more expensive than approximation test functions using a simple $p$-enriched space for $V$. We approach this from a different perspective, looking instead for robust test norms which do not induce boundary layers in the approximation of optimal test functions, and do so by formulating a general approach to analyzing the behavior of DPG under a given test norm.

@@

\subsection{Adjoint stability}

\textcolor{red}{introduce the three lemmas}
An important relationship is the duality of the energy norm and test norm; for any choice of energy norm, the test norm $\|v\|_V$ inducing it can be recovered via duality
\begin{align}
\| v \|_V = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_E} \label{norm_duality}
\end{align}
The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.

We will use the notation $\lesssim$ to denote an $\epsilon$-independent bound.

@@

Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
\[
\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
\]
where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$.

@@

>>>>

Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization.  Given some variational form $b(u,v) - l(v)=0$, the problem is modified by adding to the bilinear form a factor of the residual $r(v) = b(u,v) - l(v)=0$, scaled by a stabilization constant $\tau$.  The most well-known example of this is the streamline-upwind Petrov-Galerkin method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.

The addition of residual-based stabilization terms can also be interpreted as a modification of the test functions - in other words, stabilization can be achieved by changing the test space for a given problem.  This idea can be generalized under the idea of \textit{optimal test functions}.

%\textcolor{red}{add bit about SUPG/residual-based stabilization terms and test functions}

@@

The DPG (discontinuous Petrov-Galerkin) method is the combination of the concept of computable optimal test functions with the so-called ``ultra-weak formulation", where the regularity requirement on each solution variable is relaxed through integration by parts.  Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.  The result is a hybridized DG method with locally supported optimal test functions.  For a given operator equation $Au = f$, the ultra-weak formulation is 
\[
b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, [v] \rangle - (u,A^*v) - (f,v) = 0
\]
where $A^*$ is the formal adjoint resulting from integration by parts, and $[v]$ is the jump of $v$ across element boundaries.

\subsection{Induced norms}

An important relationship is the duality of the energy norm and test norm; under the assumption of injectivity of the adjoint of our variational 	operator $B$, for any choice of energy norm on $U$, the test norm $\|v\|_V$ inducing it can be recovered via duality
\begin{align}
\| v \|_{V,U} = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_U} \label{norm_duality}
\end{align}
If the solution is in $U$, then choosing $\|v\|=\|v\|_{V,U}$ implies $\|u\|_E = \|u\|_U$. The proof is simple; we have by definition that $b(u,v) \leq \|u\|_U\|v\|_{V,U}$. The reverse $b(u,v) \leq \|u\|_U\|v\|_{V,U}$ is proved by
\[
\inf_{u\in U} \frac{\|u\|_E}{\|u\|_U} = \inf_{u\in U} \sup_{v\in V}\frac{b(u,v)}{\|v\|_{V,U}\|u\|_U} = \inf_{v\in V} \sup_{u\in U}\frac{b(u,v)}{\|v\|_{V,U}\|u\|_U} = \inf_{v\in V} \frac{\|v\|_{V,U}}{\|v\|_{V,U}} = 1
\]
where we're able to switch the order of $\inf$ and $\sup$ due to the injectivity of $B$ (see  \cite{BabuskaEquivBrezzi}).

As a consequence of \eqref{norm_duality}, given two norms on $U$, $\|\cdot\|_{U_1}$ and $\|\cdot\|_{U_2}$, if $\|u\|_{U_1} \leq \|u\|_{U_2}$, we have the equivalent statement
\begin{align*}
\| v \|_{V,U_1} = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_{U_1}} \geq  \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_{U_2}} = \| v \|_{V,U_2} 
\end{align*}
In other words, showing an inequality between two norms on $U$ is equivalent to showing the reverse inequality between the respective induced norms on $V$.

@@

The duality between test norm and variational form holds for any particular variational form, though it is often difficult to determine analytically the form of $\|v\|_{V,U}$.  However, for the DPG ultra-weak formulation, there is an important test norm that results from a specific induced norm on $U$.  
Define the norm on $U$
\[
\|u\| = C_1\|u\|_{L^2} + C_2\|\widehat{u}\|
\]
where the norm on $\widehat{u}$ is taken to be the minimum energy extension norm
\[
\|\widehat{u}\| = \inf_{w\in V, \left.w\right|_{\Gamma_h}=\widehat{u}} \|w\|_V
\]
Then, the induced test norm is 
\begin{align*}
\|v\|_{\rm opt} &= \sup_{u,\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle - (u,A^*v)}{C_1\|u\|_{L^2} + C_2\|\widehat{u}\|} \\
&\leq \frac{1}{C_1}\sup_{u} \frac{(u,A^*v)}{\|u\|_{L^2}} + \frac{1}{C_2}\sup_{\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle}{\|\widehat{u}\|}\\
&= \frac{1}{C_1}\|A^*v\|_{L^2} + \frac{1}{C_2}\sup_{\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle}{\|\widehat{u}\|}
\end{align*}
where we have used the Cauchy-Schwarz inequality, and eliminated the supremum by noting the inequality is tight.  We define $\|u\|_{\rm opt}$ as such a norm with $C_1=C_2 = 1$,
\[
\|u\|_{\rm opt} = \|u\|_{L^2} + \|\widehat{u}\|.
\]
This is, in some sense, the ideal or ``optimal" test norm; given any particular norm $\|u\|_U$, DPG under the optimal test norm will return the best finite element approximation in both field and flux variables, independently of any parameters

The norm $\|v\|_{\rm opt}$ is non-localizable, however - the above ``optimal" test norm is induced by an inner product; however, this inner product is a global one due to the presence of the jump terms.  Solving for optimal test functions under this optimal norm through inversion of this inner product  will result in expensive global problems, making this an impractical norm to work with.

In practice, an approximation is made by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables, producing so-called \textit{quasi-optimal} test norm
\[
\|v\|_{\rm qopt} \coloneqq \|A^*v\|_{L^2} + \alpha \|v\|_{L^2}
\]
where $\alpha \in \mathbb{R}$ is chosen to complete the seminorm defined by $\|A^*v\|_{L^2}$.  This optimal test norm has been shown to induce a well-posed DPG method for any well-posed ultra-weak formulation in the context of Friedrichs' systems of equations \cite{DPGFriedrichs}.

The DPG method is currently being analyzed for both acoustic and elastic waves in context of the Helmholtz equation and equations of linear elasticity.  Numerically, DPG appears to provide a ``pollution-free" method without phase error for these problems under the ``quasi-optimal" test norm with a specific scaling of the regularizing $L^2$ terms \cite{DPG4}. Similar results have also been obtained with the quasi-optimal test norm in the context of the elasticity \cite{DPGElas} and linear Stokes equation \cite{Camellia}.

@@

We can now translate the above abstract language to a concrete model problem in computational fluid dynamics.  We consider the model convection-diffusion problem on domain $\Omega$ with boundary $\Gamma$
\begin{align}
\div (\beta u) - \epsilon\Delta v &= f  \label{primal}
\end{align}
in first order form
\begin{align*}
\div (\beta u - \sigma) &= f  \\
\frac{1}{\epsilon}\sigma - \grad u &= 0
\end{align*}
with the corresponding variational form 
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle 
\end{align*}
where $\left[ \tau_n \right]$ and $\left[ v\right]$ denote the jumps in $\tau_n$ and $v$, defined as
\begin{align*}
\left[ \tau_n \right] &= \tau^+ \cdot n^+ + \tau^-\cdot n^-\\
\left[ v\right] &= v^+{\rm sgn}(n^+) + v^-{\rm sgn}(n^-)
\end{align*}
Additionally, the inner products are taken element-wise over the finite element mesh $\Omega_h$, and the duality pairings are taken on $\Gamma_h$, the mesh ``skeleton", or union of edges of elements $K$ in $\Omega_h$.  The divergence and gradient operators are likewise understood to act element-wise.

@@

Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we can now also define the trace norms as (canonical) minimum energy extension norms (taking into account the respective lifts of $\widehat{u}$ and $\widehat{f}_n$ on $\Gamma_+$ and $\Gamma_-$, respectively)
\begin{align*}
\|\widehat{u}\| &= \inf_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gamma_h\setminus \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}\\
\|\widehat{f}_n\| &= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}= 0, \left. q\cdot n \right |_{\Gamma_h} = \widehat{f}_n} \|q\|_{H({\rm div},\Omega)}
\end{align*}
Additionally, throughout the rest of this work, we denote norms on $u$ and $\sigma$ as
\begin{align*}
\|u\| &= \|u\|_{L^2} \\
\|\sigma\| &= \|\sigma\|_{L^2}
\end{align*}
We will construct norms on $U$ as combinations of norms on each variable
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
\]
\subsection{Norms on $V$}

%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega_h$. 
As $\tau \in H({\rm div},\Omega_h)$ and $v \in H^1(\Omega_h)$, we will construct norms on $v$ and $\tau$ using some combination of terms which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$ norm over a single element
\[
\|\left(\tau,v\right)\|_{H^1(K) \times H({\rm div},K)} = \|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2  + \|\tau\|_{L^2(K)}^2 + \|\div \tau\|_{L^2(K)}^2
\]
The squared norm over the entire triangulation $\Omega_h$ is defined to be the squared sum of contributions from each element.  The exact norms that we will place on $V$ will be determined later.

The norms on the skeleton $\Gamma_h$ for $v$ and $\tau$ are defined by duality from the bilinear form
\begin{align*}
\|[\tau\cdot n]\| &= \|[\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
\|[v]\|&=\|[v]\|_{\Gamma_h^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div};\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
\end{align*}

@@

For convection-diffusion, the quasi-optimal test norm is 
\[
\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v \|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 + C_1\|v\|_{L^2} + C_2\|\tau\|_{L^2}
\]
for some choice of constants $C_1$ and $C_2$.  
%We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.  
However, use of this norm for the convection-diffusion problem is difficult - the variational problem for optimal test functions using the quasi-optimal test norm is equivalent to a reaction-diffusion system \cite{DBLP:journals/procedia/NiemiCC11}.  Transforming the problem to the reference element reveals that the inversion of the inner product associated with the optimal test norm will induce strong boundary layers of width $\epsilon/h^2$ in the optimal test functions.  In comparison, in Helmholtz and wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in smooth optimal test functions that are much easier to approximate over the reference element.  As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on partially under-resolved meshes is unavoidable, and the approximability of the optimal test functions must be addressed to take advantage of the properties of DPG.

In the application of DPG in \cite{DPG1,DPG2,DPG3,DPG4}, the approximation of optimal test functions is done using the enriched test space $V = \cup_{K} P^{p+\Delta p}(K)$, where $p$ is the polynomial order of the trial space on a given element $K$.  In other words, optimal test functions are approximated element-by-element using polynomials whose order is $\Delta p$ more than the local order of approximation.  Under this scheme, the approximation of optimal test functions is tied to the effectiveness of the $p$-method.  Unfortunately, for problems with boundary layers (including the approximation of optimal test functions under the quasi-optimal test norm), the $p$-method performs very poorly.

Resolving such boundary layers for an underresolved mesh has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.  However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is difficult and far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$. We approach this from a different perspective, looking instead for robust test norms which do not induce boundary layers in the approximation of optimal test functions, and do so by formulating a general approach to analyzing the behavior of DPG under a given test norm.

@@

\section{Strategy for proving robustness under a given test norm}

The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm \textit{that does not lose robustness as $\epsilon \rightarrow 0$}.  The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
\[
\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
\]
Ensuring that each term $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ is of the same order will allow for smooth solutions (under some assumptions on $\beta$).  
\textcolor{red}{Why are we allowed to have $\beta\cdot \grad v$ of order 1 while we have other terms of order $O({\rm Pe})$?  Why does this term not induce boundary layers?}

Showing the second condition on robustness is equivalent to showing the robust equivalence of the $L^2$ error of the solution in a norm on $U$ (that does not grow as $\epsilon\rightarrow 0$) times the error in the energy norm
\[
\left(\|u\| + \|\sigma\| + \|\widehat{u}\| + \|\widehat{f}_n\|\right) \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left(\|u\| + \|\sigma\| + \|\widehat{u}\| + \|\widehat{f}_n\|\right)
\]
where $\lesssim$ denotes a bound by a constant that will not grow as $\epsilon \rightarrow 0$.  
%$\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_U \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E$.  
Our strategy for proving such a bound is broken down into three parts.

\subsection{Translate equivalence norms on $U$ to norms on $V$}

We begin with a given norm on $U$
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
\]
By \eqref{norm_duality}, the duality of test norm and energy norm, a norm of this form induces the test norm
\begin{align*}
\|\left(v,\tau\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0}}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
& \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_4}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|}
\end{align*}
where $f$ and $g$ are defined as 
\begin{align*}
g &\coloneqq \div \tau - \beta \cdot \grad v\\
f &\coloneqq \epsilon^{-1}\tau + \grad v
\end{align*}
which, by definition of the boundary norms, gives the characterization of the induced test norm 
\[
\|\left(v,\tau\right)\|_{V,U} \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\|[\tau\cdot n]\| + \frac{1}{C_4}\|[v]\|
\]
\textcolor{red}{is this an equality? Is the inequality attainable, and thus attained in the supremum?} We can now use this relation to compare two different norms on $U$ by comparing their induced norms on $V$.  Additionally, showing a robust inequality between two norms on $U$ is similarly equivalent to showing the robust reverse inequality in the induced norms on $V$.

\subsection{Decomposition into analyzable components}

After reducing the problem of comparing norms on $U$ to comparing norms on $V$, we break the analysis of $\left(\tau,v\right) \in V$ into the analysis of subproblems.  Define the decomposition
\[
\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
\]
where $\left(v_1,\tau_1\right)$ satisfies 
\begin{align*}
\epsilon^{-1}\tau_1 + \grad v_1 &= 0\\
\div \tau_1 - \beta\cdot \grad v_1 &=  \div \tau - \beta\cdot \grad v = g,
\end{align*} 
Likewise, we define $\left(v_2,\tau_2\right)$ as satisfying
\begin{align*}
\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f\\
\div \tau_2 - \beta\cdot \grad v_2 &= 0
\end{align*}
We will additionally require both $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$ to come from $H({\rm div}, \Omega)\times H^1(\Omega)$, and to satisfy boundary conditions
\begin{align*}
\tau_i\cdot n &= 0, \quad x \in \Gamma_-\\
v_i &= 0, \quad x \in \Gamma_+
\end{align*}
for $i = 1, 2$.  The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific above boundary conditions removes the contribution of the jump terms over the skeleton $\Gamma_h$ in the bilinear form, allowing us to bound components of the induced test norm separately from each other.

Finally, by construction, $\left(v_0,\tau_0\right)$ must satisfy 
\begin{align*}
\epsilon^{-1}\tau_0 + \grad v_0 &= 0\\
\div \tau_0 - \beta\cdot \grad v_0 &= 0
\end{align*}
with jumps
\begin{align*}
[v_0] &= [v], \quad x\in \Gamma_h^0\\
[\tau_0 \cdot n] &= [\tau \cdot n], \quad x\in \Gamma_h^0.
\end{align*}
By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
\begin{align}
v_0 &= v, \quad x\in \Gamma_+ \label{bc_1}\\
\tau_0 \cdot n &= \tau \cdot n, \quad x\in \Gamma_-\cup \Gamma_0. \label{bc_2}
\end{align}

We have now decomposed any arbitrary test function $\left(\tau,v\right)$ into a single discontinuous portion and two conforming portions.  Showing robust equivalence of $\|\left(v,\tau\right)\|_V$ with another norm $\|\cdot \|_{?}$ on $V$ reduces to showing robust equivalence of each component 
\[
C_1\|\left(\tau,v\right)\|_{?} \lesssim \|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim C_2\|\left(\tau,v\right)\|_{?}
\]
Bounding $\|\left(\tau_0,v_0\right)\|$ requires the use of techniques and decompositions first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{DPGrobustness}.  However, due to the conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$, the bound from above of test functions $\|\left(\tau_{1,2},v_{1,2}\right)\| \leq C\|g\|$ is reduced to proving classical error estimates for the adjoint equation
\begin{align*}
\epsilon^{-1}\tau + \grad v &= f\\
\div \tau - \beta\cdot \grad v &=  g,
\end{align*} 
for data $f, g\in L^2({\Omega_h})$ and boundary conditions $\left.\tau\cdot n\right|_{\Gamma_-} = 0$ and $\left.v\right|_{\Gamma_+} = 0$

\subsection{Deriving adjoint estimates}

The final step to constructing a robust, localizable test norm on $V$ that does not generate boundary layers is to derive adjoint stability estimates on $\tau$ and $v$ in terms of localizable normed quantities.  These normed quantities will create ``building-blocks" through which we can construct test norms, where each building block will correspond roughly to the control of $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.

We introduce first the bounds derived; the proofs will be given later.  Under specific assumptions on $\beta$, we have the robust bounds
\begin{itemize}
\item For $f=0$ and $v \in H^1(\Omega_h)$, satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}
\begin{align*}
\|\beta \cdot \grad v \| &\lesssim \| g\| 
\end{align*}
\item For $v \in H^1(\Omega_h)$ and satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$
\begin{align*}
\epsilon \|\grad v\|^2 + \|v\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
\end{align*}
\item For $f=g=0$, 
\begin{align*}
\|\grad v\| = \frac{1}{\epsilon}\|\tau\| &\lesssim \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
\end{align*}
\end{itemize}
Together, these estimates will be sufficient to complete the first step and demonstrate bounds on induced test norms for different scalings of norms on $U$.

\section{Actually proving things}

@@

Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
\[
\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
\]
where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.

@@

\textcolor{red}{Move this to after the proof of the streamline gradient lemma.}
